Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-03 article.tex
wording

Note that this matrix is symmetric
and thus it is impossible to determine the causal mechanism behind the
interaction (I directly causes J, J directly causes I or both
[de la Fuente, 2004])\footnote{Two other causal mechanisms may be implied
by a non-zero partial coefficient. First, the pair of variables may be induced
by a common (hidden) variable and second, I (respectively J) is conditionally
correlated to a hidden variable affecting J (resp. I) [de la Fuente, 2004].}

>>>>

%  Partial correlation => Symmetric measure
Since this matrix is symmetric, it is not possible to infer the causal
mechanism behind the interaction (I directly causes J, J directly causes I or
both [de la Fuente, 2004]). Futhermore two other causal mechanisms may be implied
by a non-zero partial coefficient. First, the pair of variables may be induced
by a common (hidden) variable and second, I (respectively J) is conditionally
correlated to a hidden variable affecting J (resp. I) [de la Fuente, 2004].
